Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-05-06 longSC.tex
finish ante comment 1st

%\begin{figure*}[!]
%            \begin{center}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_EKRT.eps}}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_EKRT.eps}}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_EKRT.eps}}
%              \end{center}
%        \caption{Measurements of  SC(5,2) (a), SC(5,3) (b) and SC(4,3) (c) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}        
%        \label{fig:Figure_5}
%\end{figure*}
The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.  All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of all order SC($m$,$n$) observables shown on the left panels in Fig.~\ref{fig:Figure_4}.
Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured but it cannot describe the data quantitively for most of the centrality ranges.
Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 0--10\% central collisions. The NSC(3,2) observable does not show sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
However, NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
Even though NSC(4,2) favors both AMPT initial conditions with $\eta/s=0.08$ and MC-Glauber initial conditions with $\eta/s=0.20$,
SC(4,2) can only be described by models with smaller $\eta/s$. Hence the calculation with large $\eta/s=0.20$ is ruled out. We conclude that $\eta/s$ should be small and that AMPT initial conditions are favored by the data.
The NSC(5,2) and SC(5,3) observables are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0--10\% central collisions. The NSC(4,3) observable shows sensitivity to both initial conditions and $\eta/s$ parameterizations.
% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations.
The SC(4,3) results are clearly favored by smaller $\eta/s$ values but NSC(4,3) cannot be described by these models quantitively.

@@

The SC($m$,$n$) and NSC($m$,$n$) observables calculated from AMPT simulations are compared with data in Fig.~\ref{fig:Figure_5}.
For SC(3,2), the calculation with the default AMPT settings is closest to the data, but none of the AMPT configurations can describe the data fully. 
The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations fail to describe either of them in the most central collisions.
Interestingly, the string melting AMPT configuration cannot reproduce the data, and the resulting correlations are weaker than in data.
The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
The hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but not enough to describe the data.
Further investigations proved why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2). By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, it was possible to recover the difference in SC(3,2) between the data and the model. The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values as reported in \cite{Adam:2016nfo} in all centrality ranges.

In the case of SC(4,2), the string melting AMPT model can describe the data fairly well while the default model underestimates it.
The NSC(4,2) observable is slightly overestimated by the string melting setting which can describe SC(4,2) but the default AMPT configuration can describe the data better.
The influence of the hadronic rescattering phase on NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)). The hadronic rescattering makes NSC(4,2) slightly smaller.
It should be noted that the agreement with SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between the AMPT models and the data as was demonstrated for SC(3,2).
Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints on the parameters in AMPT models.
The string melting AMPT model describes SC(5,3) and NSC(5,3) well. However, the same setting overestimates SC(5,2) and NSC(5,2). 
The default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as in the case of NSC(3,2) and NSC(4,2).
% interesting AMPT String Melting OFF, Rescattering ON < AMPT String Melting ON, Rescattering OFF
In the case of SC(4,3), neither of the settings can describe the data but the default AMPT model comes the closest to the data. 
The string melting AMPT model fails to describe SC(4,3) and NSC(4,3).
In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC$(m,n)$) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(5,2) and predicts a very weak correlation in NSC(4,3).

@@

As discussed in Sec.~\ref{sec:results}, a hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors and NSC(5,2) is smaller than NSC(5,3) while SC(5,2) is larger that SC(5,3).
Except for the 0--10\% centrality range, we found that the same hierarchy also holds in the hydrodynamic calculations and the AMPT models explored in this article.
The observed reversal of the hierarchy SC(5,2) $>$ SC(5,3), can be explained by the magnitudes of the individual flow harmonics ($v_2$ $>$ $v_3$). 
The opposite trend is observed for the normalized SC (NSC(5,3) $>$ NSC(5,2)). This can be attributed to the fact that flow fluctuations are stronger for $v_3$ than $v_2$~\cite{Aad:2013xma}. This was claimed in Ref.~\cite{Zhu:2016puf} and also seen in Ref.~\cite{Bhalerao:2014xra} based on an AMPT model. 
NSC($m$,$n$) correlators increase with larger $\eta/s$ in hydrodynamic calculations in the 0-30\% centrality range in the same way as the event plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}. In semi-peripheral collisions ($>$40\%), the opposite trend is observed.

We list here the important findings from the model comparisons to the centrality dependence of SC($m$,$n$) and NSC($m$,$n$):
\begin{enumerate}[(i)]
	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively but it cannot describe the data quantitively for most of the centrality ranges.
	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations.
	\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.

@@

It can be seen in Fig.~\ref{fig:Figure_2} that for NSC(3,2) there is no $p_{\rm T, min}$ dependence in the centrality range $<$30\%, and a moderate decreasing trend with increasing $p_{\rm T, min}$ is observed in the $>$30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T, min}$ or centrality increases.

@@

The NSC(3,2) and NSC(4,2) observables as a function of $p_{\rm T, min}$ are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}, respectively.
The observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is also seen in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
With the exception of the default configuration, the other AMPT settings predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitudes of both NSC(3,2) and NSC(4,2) simultaneously.
In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and shows a stronger $p_{\rm T}$ dependence than the data.
As for  NSC(4,2), the same model which describes NSC(3,2) can also reproduce the data well except for the $10-20\%$ and $40-50\%$ centralities where some deviations are observed.
When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength are weakened by the hadronic rescattering.
This might imply that hadronic interactions are the source of this observed $p_{\rm T}$ dependence even though the relative contributions from the partonic and hadronic stages in the final state particle distributions should be studied further.

>>>>

%\begin{figure*}[!]
%            \begin{center}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_EKRT.eps}}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_EKRT.eps}}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_EKRT.eps}}
%              \end{center}
%        \caption{Measurements of  SC(5,2) (a), SC(5,3) (b) and SC(4,3) (c) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}        
%        \label{fig:Figure_5}
%\end{figure*}
The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.  All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of all order SC($m$,$n$) observables shown on the left panels in Fig.~\ref{fig:Figure_4}.
Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured but it cannot describe the data quantitively for most of the centrality ranges.
Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 0--10\% central collisions. The NSC(3,2) observable does not show strong sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
However, NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
Even though NSC(4,2) favors both AMPT initial conditions with $\eta/s=0.08$ and MC-Glauber initial conditions with $\eta/s=0.20$,
SC(4,2) can only be described by models with smaller $\eta/s$. Hence the calculation with large $\eta/s=0.20$ is ruled out. We conclude that $\eta/s$ should be small and that AMPT initial conditions are favored by the data.
The NSC(5,2) and NSC(5,3) observables are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0--10\% central collisions. The NSC(4,3) observable shows sensitivity to both initial conditions and $\eta/s$ parameterizations.
% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations.
The SC(4,3) results are clearly favored by smaller $\eta/s$ values but NSC(4,3) cannot be described by these models quantitively.

@@

The SC($m$,$n$) and NSC($m$,$n$) observables calculated from AMPT simulations are compared with data in Fig.~\ref{fig:Figure_5}.
For SC(3,2), the calculation with the default AMPT settings is closest to the data, but none of the AMPT configurations can describe the data fully. 
The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations fail to describe either of them in the most central collisions.
%Interestingly, the string melting AMPT configuration cannot reproduce the data, and the resulting correlations are weaker than in data.
The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
The hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but not enough to describe the data.
Further investigations proved why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2). By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, it was possible to recover the difference in SC(3,2) between the data and the model. The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values as reported in \cite{Adam:2016nfo} in all centrality ranges.

In the case of SC(4,2), the string melting AMPT model can describe the data fairly well while the default model underestimates it.
The NSC(4,2) observable is slightly overestimated by the string melting setting which can describe SC(4,2) but the default AMPT configuration can describe the data better.
The influence of the hadronic rescattering phase on NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)). The hadronic rescattering makes NSC(4,2) slightly smaller.
It should be noted that the agreement with SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between the AMPT models and the data as was demonstrated for SC(3,2).
Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints on the parameters in AMPT models.
The string melting AMPT model describes SC(5,3) and NSC(5,3) well. However, the same setting overestimates SC(5,2) and NSC(5,2). 
The default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as in the case of NSC(3,2) and NSC(4,2).
% interesting AMPT String Melting OFF, Rescattering ON < AMPT String Melting ON, Rescattering OFF
In the case of SC(4,3), neither of the settings can describe the data but the default AMPT model comes the closest to the data. 
The NSC(4,3) observable is well described by the default AMPT model but cannot be reproduced by the string melting AMPT model.
In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC$(m,n)$) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(4,2) and NSC(5,2) and predicts a very weak correlation both for NSC(4,2) and NSC(4,3).

@@

As discussed in Sec.~\ref{sec:results}, a hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>~20\%$ within the errors.
Except for the 0--10\% centrality range, we found that the same hierarchy also holds in the hydrodynamic calculations and the AMPT models explored in this article.
While NSC(5,2) is smaller than NSC(5,3), SC(5,2) is larger than SC(5,3).
The observed reversal of the hierarchy SC(5,2) $>$ SC(5,3), can be explained by the magnitudes of the individual flow harmonics ($v_2$ $>$ $v_3$). 
This can be attributed to the fact that flow fluctuations are stronger for $v_3$ than $v_2$~\cite{Aad:2013xma}. This was claimed in Ref.~\cite{Zhu:2016puf} and also seen in Ref.~\cite{Bhalerao:2014xra} based on an AMPT model. 
NSC($m$,$n$) correlators increase with larger $\eta/s$ in hydrodynamic calculations in the 0-30\% centrality range in the same way as the event plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}. In semi-peripheral collisions ($>$~40\%), the opposite trend is observed.

We list here the important findings from the model comparisons to the centrality dependence of SC($m$,$n$) and NSC($m$,$n$):
\begin{enumerate}[(i)]
	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively but it cannot describe the data quantitively for most of the centrality ranges.
	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations.
	\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>~20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.

@@

It can be seen in Fig.~\ref{fig:Figure_2} that for NSC(3,2) there is no $p_{\rm T, min}$ dependence in the centrality range $<$~30\%, and a moderate decreasing trend with increasing $p_{\rm T, min}$ is observed in the $>$~30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T, min}$ or centrality increases.

@@

The NSC(3,2) and NSC(4,2) observables as a function of $p_{\rm T, min}$ are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}, respectively.
The observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is also seen in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
With the exception of the default configuration, the other AMPT settings predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitudes of both NSC(3,2) and NSC(4,2) simultaneously.
In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40--50\%$ where the model underestimates the data and shows a stronger $p_{\rm T}$ dependence than the data.
As for  NSC(4,2), the same model which describes NSC(3,2) can also reproduce the data well except for the $10--20\%$ and $40--50\%$ centralities.
When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength are weakened by the hadronic rescattering.
This might imply that hadronic interactions are the source of this observed $p_{\rm T}$ dependence even though the relative contributions from the partonic and hadronic stages in the final state particle distributions should be studied further.
